\sysfull

### 2018-04-17 paper/intro.tex
fig 1 to 0.4 column
intro: tighten the contribs

\begin{wrapfigure}{t!}{0.5\textwidth}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}

@@

\item The first {\em adaptive} task-based intermittent execution model that dynamically coalesces tasks to avoid unnecessary commit overhead. 
\item The first power interrupts immune memory virtualization mechanism for an intermittent system that \sys uses to preserve the atomicity of coalesced tasks.
\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.

@@

\item An evaluation directly comparing \sys to a state of the art task-based intermittent programming and execution model from prior work, showing that on a suite of benchmarks from the literature and several new workloads, \sys often has higher performance and is more flexible to diverse energy conditions. 

@@

Sections~\ref{sec:task_adaptation} describe \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are give in Section~\ref{sec:implementation}. Section~\ref{sec:discussion} discusses \sys
design issues. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe
\sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the

>>>>

\begin{wrapfigure}{t!}{0.4\textwidth}
    \centering
    \includegraphics[width=0.4\textwidth]{figures/intro-figure.pdf}
    \caption{Task coalescing at runtime reduces time and energy overhead in task-based intermittent programming models by performing fewer commits (denoted as \texttt{cmt} in the figure). On the other hand, task splitting reduces wasted computation and enables termination for bigger tasks.}
    \label{fig:coalesce}
\end{wrapfigure}

@@

\item The first {\em adaptive} task-based intermittent execution model that
dynamically \emph{coalesces} tasks to reduce commit overhead and
\emph{downscales} tasks to ensure forward progress.
\item The first memory virtualization mechanism that preserves the atomicity of coalesced tasks under power failures.
%\item A fall-back dynamic task splitting mechanism that preserves forward progress despite executing tasks that are too large for a device's energy supply.

@@

\item An evaluation directly comparing \sys to a state of the art task-based
intermittent programming and execution model from prior work, showing that on a
suite of benchmarks from the literature and several new workloads, \sys often
has higher performance and is more flexible to diverse energy conditions. 

@@

Sections~\ref{sec:task_adaptation} describe \sys's task adaptation mechanism (coalescing and downscaling). Memory virtualization mechanism is provided in Section~\ref{sec:memory_virtulaization}. Implementation details of \sys are give in Section~\ref{sec:implementation}. Sections~\ref{sec:methodology} and~\ref{sec:evaluation} describe \sys's methodology and evaluation, respectively. Section~\ref{sec:related_work} puts \sys in the
